---
title: "Simple document"
author: "Dhriti Iyer"
output: 
  html_document:
    toc: true
    toc_float: true
---

I'm an R Markdown document! 

# Section 0: libraries

```{r load_libraries, message=FALSE}
library(tidyverse)
```

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

```{r setup, include = FALSE}
library(tidyverse)
```
```{r df_create}
set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = 0.5),
  y = 1 + 2 * x + rnorm(1000)
)
```

```{r x_hist}
ggplot(plot_df, aes(x = x)) +
  geom_histogram()
```

# Section 5: Learning Assessment

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r}
la_df = tibble(
  num_var = rnorm(n = 500, mean = 1),
  log_var = num_var > 0,
  abs_var = abs(num_var) 
)

ggplot(la_df, aes(x = abs_var)) + geom_histogram()
```
The median is `r round(median(pull(la_df, num_var)), 2)`


